\documentclass[a4paper,12pt]{letter}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[left=2cm, right=2cm, top=1cm, bottom=2cm]{geometry}

\begin{document}



\begin{letter}

\date{Nice, December $22^{\text{nd}}$ 2023,}


\opening{\textbf{Object :} Application for the position of teaching assistant}


Dear Sir/Madam,

I am currently a Master's student in Mathematical Engineering at the University of Côte d'Azur, and I am writing to express my interest in the position of English Language Teaching Assistant at your esteemed educational institution.

Throughout my university studies, I have developed significant communication skills in both French and English. I have had the opportunity to conduct activities in English, such as hosting ceremonies based on mathematical tools. These experiences have enhanced my understanding of language learning dynamics and intercultural communication.

My motivation for this position lies primarily in the opportunity to apply my linguistic skills in a stimulating educational context. Your institution is renowned for its commitment to academic excellence, and I am confident that my background as a mathematics student, coupled with my proficiency in English, will enable me to make a meaningful contribution to students' learning.

I would like to highlight my ability to create dynamic and interactive learning environments. My experience in leading activities in English, coupled with my ease in conveying complex concepts in an accessible manner, are strengths that I aim to leverage in an educational setting.

My academic journey and previous experiences, including my immersion internship at SODECI (Société de Distribution d'Eau de Côte d'Ivoire), have provided opportunities to refine my pedagogy and adapt to the specific needs of learners. These experiences have also allowed me to develop the ability to work collaboratively and communicate effectively with a diverse audience.

I am convinced that my passion for teaching, proficiency in the English language, and communication skills make me an ideal candidate to contribute to your teaching team.

I am available for an interview to discuss my application further and how my skills align with the specific needs of your institution. Please accept, Sir/Madam, the expression of my distinguished regards.


\closing{Cordially,\\

KRA Kouamé Gérard}



\end{letter}
\end{document}